DATA 621 - Business Analytics and Data Mining

### 2020-11-20 HW5/HW5-Draft.Rmd
Finish Poisson Section. Sketch out remaining skeleton

# Melt them from wide to long format
predictorDTM <- melt(predictorDT, variable.name = 'metric',
                     value.name = 'value',  variable.factor = FALSE,
                     id.vars = NULL)

@@

```{r model1impute}
# Create bagged-tree imputation model
m1trnXi <- preProcess(m1trnX, method =c('nzv', 'bagImpute'))

@@

# Melt them from wide to long format
m1predictorDTM <- melt(m1predictorDT, variable.name = 'metric',
                     value.name = 'value',  variable.factor = FALSE,
                     id.vars = NULL)

@@

# BUILD MODELS
## Modeler # 1
Each of the models will follow a similar format, with only the family changing.
Each model will start with the saturated model including all the predictors,
***except*** for `STARS` which will be replaced with the interaction between
`Rated` and `STARS`. A forward and backwards stepwise procedure based on AIC
will be used, and the model with the lowest AIC on the training set will be the
selected to be tested against the testing set. Using stepAIC precludes the use
of k-fold cross validation.

@@

### Poisson Model

```{r m1Poisson}
set.seed(350047)
m1PFit <- train(TARGET ~ . - INDEX - STARS + Rated:STARS, data = m1trnXimp,
                trControl = trc, method = 'glmStepAIC',
                family = poisson(link = 'log'), direction = 'both', trace = 0)
# Print results
kable(summary(m1PFit$finalModel)$coefficients, digits = 3L,
      caption = "Model 1 Poisson Regression Output")
```

```
                     Df Deviance   AIC
<none>                    9654.5 31998
- Sulphates           1   9657.1 31998
+ Density             1   9654.1 31999
+ ResidualSugar       1   9654.2 31999
- Alcohol             1   9658.3 32000
+ CitricAcid          1   9654.4 32000
+ FixedAcidity        1   9654.4 32000
- pH                  1   9659.0 32000
- Chlorides           1   9659.5 32001
- FreeSulfurDioxide   1   9659.7 32001
- TotalSulfurDioxide  1   9670.3 32012
- VolatileAcidity     1   9670.9 32012
- AcidIndex           1   9880.9 32222
- LabelAppeal         1  10102.7 32444
- `STARS:RatedRated`  1  10335.1 32676
- RatedRated          1  10337.5 32679
```

# SELECT MODELS
## Model Selection Criteria
We will look at RMSE and AIC as our metrics and select the model which performs
best on both, Ties will be broken by \(R^2\).

# References

@@

# CODE APPENDIX
```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
```{r loadData}
```
```{r missingVal}
```
```{r statsN}
```
```{r graphsD}
```
```{r graphsH}
```
```{r corrgram}
```
```{r trainTestSplit}
```
```{r model1addVars}
```
```{r model1impute}
```
```{r m1postImputeD}
```
```{r m1postImputeH}
```
```{r m1TrainControl}
```

>>>>

# Melt them from wide to long format
predictorDTM <- melt(predictorDT, variable.name = 'metric',
                     value.name = 'value',  variable.factor = FALSE,
                     measure.vars = nmtrn)

@@

```{r model1impute}
# Create bagged-tree imputation model
set.seed(89)
m1trnXi <- preProcess(m1trnX, method =c('nzv', 'bagImpute'))

@@

# Melt them from wide to long format
m1predictorDTM <- melt(m1predictorDT, variable.name = 'metric',
                     value.name = 'value',  variable.factor = FALSE,
                     measure.vars = nmtrn)

@@

# BUILD MODELS
## Model Set # 1
The same person is building one of each requested model. Each of the models will
follow a similar format, with only the family changing. Each model will start
with the saturated model including all the individual predictors ***except***
for `STARS`. There will also be the following interactions:

  * `Rated` and `STARS`
    * As discussed above, by having `Rating` on its own and this interaction
    the effect of both having a rating and the effect of the rating level can be
    measured, without penalizing unrated wines a second time for a 0.
  * The full four-way interaction between `AcidIndex`, `FixedAcidity`,
  `VolatileAcidity`, and `pH`
    * There are **four** separate predictors relating to acidity. Despite their
    Pearson product-moment correlations being low, I am suspicious of too much
    weight being given to acidity. By including their interactions, effects can
    be tempered, or magnified, as necessary. `CitricAcid` is not included here
    as is not merely an acid but a flavor provider as well. Also, five-way
    interactions lead to migraines.
  * `FreeSulfurDioxide` and `TotalSulfurDioxide`
    * Again, a case of multiple theoretically related predictors

A forward and backwards stepwise procedure based on AIC will be used, and the
model with the lowest AIC on the training set will be the selected to be tested
against the testing set. Using stepAIC precludes the use of k-fold cross
validation.

@@

### Poisson Model # 1

```{r m1PTrain}
set.seed(350047)
m1PFit <- train(TARGET ~ . + FreeSulfurDioxide:TotalSulfurDioxide +
                  AcidIndex * FixedAcidity * VolatileAcidity * pH +
                  Rated:STARS - INDEX - STARS, data = m1trnXimp,
                trControl = trc, method = 'glmStepAIC',
                family = poisson(link = 'log'), direction = 'both', trace = 0)
# Save AIC
m1PFitAIC <- AIC(m1PFit$finalModel)
```
\small
```{r m1PTable}
# Print results. This needed to ne in its own section so that the LaTeX commands
# to change the text size can be wrapped around it.
kable(summary(m1PFit$finalModel)$coefficients,
      caption = "Model 1 Poisson Regression Output")
```
\normalsize

#### Coefficient Discussion
The absolute magnitude of the coefficients makes sense. Factors related to
acidity tend to lower the number of cases bought. The factors with the greatest
magnitude effect are all positive, and they are being rated, the rating level,
and the label appeal. Keeping everything else equal, merely being rated
increases the number of cases by about \(e^{0.6509117} \approx  1.9\)!

All the coefficients are significant at at least the 5% level except for
Sulphates, but in terms of AIC, leaving it in provided a better model than
taking it out

#### Variable Importance
The further down the list below a variable preceded by a `-` is, the more
important it is, as its removal would cause a greater disruption to the
deviance and the AIC. The three rating variables, being rated, the rating level,
and the label appeal, are the most important variables when it comes to future
case purchases.

It is also interesting to note that the model including `VolatileAcidity` as 
a singleton predictor has a lower deviance than the selected model, but that the
drop in deviance is not enough to offset the possible parameter error. However,
it makes itself felt through its interaction with `AcidIndex` in the selected
model.
```
                                              Df Deviance   AIC
<none>                                             9644.0 31993
+ VolatileAcidity                              1   9642.4 31994
- Sulphates                                    1   9646.5 31994
- `FreeSulfurDioxide:TotalSulfurDioxide`       1   9647.1 31994
+ pH                                           1   9643.5 31995
+ Density                                      1   9643.6 31995
+ ResidualSugar                                1   9643.6 31995
+ `VolatileAcidity:pH`                         1   9643.7 31995
+ CitricAcid                                   1   9643.9 31995
- Alcohol                                      1   9647.9 31995
+ `FixedAcidity:VolatileAcidity`               1   9643.9 31995
+ `FixedAcidity:pH:AcidIndex`                  1   9644.0 31995
+ `FixedAcidity:VolatileAcidity:pH`            1   9644.0 31995
+ `VolatileAcidity:pH:AcidIndex`               1   9644.0 31995
+ `FixedAcidity:VolatileAcidity:AcidIndex`     1   9644.0 31995
+ `FixedAcidity:pH`                            1   9644.0 31995
+ `FixedAcidity:VolatileAcidity:pH:AcidIndex`  1   9644.0 31995
- FixedAcidity                                 1   9648.1 31995
- `FixedAcidity:AcidIndex`                     1   9648.4 31996
- Chlorides                                    1   9648.9 31996
- `pH:AcidIndex`                               1   9648.9 31996
- FreeSulfurDioxide                            1   9652.3 32000
- `VolatileAcidity:AcidIndex`                  1   9661.9 32009
- TotalSulfurDioxide                           1   9662.0 32009
- AcidIndex                                    1   9678.8 32026
- LabelAppeal                                  1  10092.2 32439
- `STARS:RatedRated`                           1  10322.8 32670
- RatedRated                                   1  10325.1 32672
```

### Negative Binomial Model # 1

### Multiple Linear Regrssion Model # 1

## Poisson Model #2

## Negative Binomial Model #2

## Multiple Linear Regrssion #2

# SELECT MODELS
## Model Selection Criteria
We will look at RMSE and MAE as our metrics and select the model which performs
best on both. If no model peforms best on both, the AIC of the model results on
the training set will be used to break the tie.

## Model Test Results

### Poisson Model 1

### Poisson Model 2

### Negative Binomial Model 1

### Negative Binomial Model 2

### Multiple Linear Regression Model 1

### Multiple Linear Regression Model 2

## Comparsion

## Selection

# PREDICTION

# REFERENCES

@@

# CODE APPENDIX
```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
```{r loadData}
```
```{r missingVal}
```
```{r statsN}
```
```{r graphsD}
```
```{r graphsH}
```
```{r corrgram}
```
```{r trainTestSplit}
```
```{r model1addVars}
```
```{r model1impute}
```
```{r m1postImputeD}
```
```{r m1postImputeH}
```
```{r m1TrainControl}
```
```{r m1PTrain}
```
```{r m1PTable}
```
